\chapter{Introduction}
On this project our purpose is saving navigation data of users and show the path of a trip on the map. There will be a mobile application and server side for provide some features, lets users to share trips, review trips, communicate and socialize each others. Various media records such as photos, videos and audio recordings recorded from mobile device during the trip will be shown on the route. If the journey is planned according to more than one member, there will be a team trip option for the members. This option will requires use the internet connection to share real time locations between each team member. This feature lets every team member to see any team member's location simultaneously. In order to determine travelling method, using the data temporal changes of the positions taken from the satellite, average and instant speed will calculated. As result trip type will be labelled as vehicle trip, walking trip, running trip or cycling trip using calculated speed data. If the system is operating in the guiding role, the route that the user or team wants to go will be described by system to user. A social media environment will be designed. People will be able to establish their friendship here. In the news flow, there will be a timeline section. Posts which is shared by friends of users will be shown there. The trips can be liked by other users in the news flow, it can be saved for future review, it can be suggested for other friends to visit, or the users can follow trips they like from its content by downloading it on their own mobile device.
\section{Literature Review}
Our purpose to do that project is making easier to planning, storing, sharing a trip for traveler. We know that now it is not easy to organize photos and medias taken on a trip and sharing on Facebook. In any marketplaces including play store and appstore there are a lot of applications for tracking and travel planning but most of them only saves location data not including media or user notes. There are only a few application remarkable whiches saving location data, medias and also some of them providing a social media enviroment. However there is no application that provides tracking, organizing medias, repeating someones experience, sharing memories and also doing all of these with friends at the same time. 

\section{Objective of the Thesis}
For travelers it is not easy to organize medias and associate any media with saved location. Also if trip has been organized with more than one person it is also difficult to merge medias and organize them for sharing. It's important to say that every member of team has him/her own memory which is important and it must be saved. Altough every member of a team has him/her own memory people can forget memories and need to remember them like a place that a photo taken.

\section{Hypothesis}
To do that it is neccessary to store locations data, store medias and associate medias with its own location. And store them with everthing in a trip. So that people can remember a everthing in a trip.