\chapter{General Information}
The main purpose of this section to review projects that are already developed by others which is related with ours.
\section{Trip Tracker(Android application)}
Trip Tracker\cite{triptracker}, a Microsoft Garage project, is a free application that automatically records your drives, runs, walks, and bike rides. This application has developed with LOOP\cite{loop}. Without that feature this application can only track, save user's location and show saved data on the map.

\section{Route Tracker(Android application)}
Route Tracker\cite{routetracker} is a GPS application for tracking/loading routes in your android mobile phone that gives you a real time response on your location. It supports GPX tracks file import, GPX/KML/google map embedded HTML file export,sync workouts with RunKeeper account, auto-Lap for each mile/kilometer, audio reminder for auto lap time reminding, vibration for auto lap, sharing to friends, open street view for record locations, duration, distance, pace and calories indication. This application could only track, save user's location and show saved data on the map.

\section{Polarsteps - Travel Tracker(Android and Ios application)}
Polarsteps\cite{polarsteps} can provide tracking location of user, can show media as just photo and video on the trip path. They are claim to low power consumption. In this application it is not possible to organize team trips. User can use this application only for their personal trips. This application also provides a social media platform. Social media plataform could only usable for sharig trips and comment on shared content. It is not possible to download and track any shared route.

\section{Maps (Android and Ios application)}
Google Maps\cite{googlemap} can save user's location continuosly. In this application there is no start trip option. This application determines trip kind automaticaly. In purpose this application not developed for tracking, developed for navigate users. User can wath his/her activity on the menu named 'TimeLine' (in Turkish 'Zaman Çizelgesi'). On users timeline media such as photos and videos shown not audio or any othe medias. In this application there is no social media or sharing trip option.
